\textbf{NBA Party}

### 2017-04-12 init_model.rnw
Now using 'nhours.lgame' to obtain a very significant model.

setkey(lines, season, team, date)
lines[, list(date, team, opponent, location, 
             line, score, outcome, ndays.lgame, 
             travel.dist, avg.age, nmusicians)]

@@

<<echo=-4>>= 
lines[, party := ifelse(ndays.lgame == 1, nmusicians, 0)]

m <- glm(outcome == 'W' ~ party + ndays.lgame + travel.dist + avg.age, 
         data = lines[season < 2017 & last.game.loc != team])

@@

<<>>=
m <- glm(outcome == 'W' ~ I(nmusicians*(ndays.lgame==1)), 
         data = lines[season < 2017 & last.game.loc != team])

@@

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & ndays.lgame == 1 & last.game.loc != team], 
             type = 'response')
table(round(p), lines[season == 2017 & ndays.lgame == 1 & last.game.loc != team, outcome])

>>>>

setkey(lines, season, team, date)
lines[, list(date, team, opponent, location, 
             line, score, outcome, nhours.lgame, 
             travel.dist, avg.age, nmusicians)]

@@

<<echo=-4>>=

HOURS <- 24
lines[, party := ifelse(nhours.lgame <= HOURS, nmusicians, 0)]

m <- glm(outcome == 'W' ~ party + nhours.lgame + travel.dist + avg.age, 
         data = lines[season < 2017 & last.game.loc != team])

@@

<<>>=
HOURS <- 24
m <- glm(outcome == 'W' ~ I(nmusicians*(nhours.lgame <= HOURS)), 
         data = lines[season < 2017 & last.game.loc != team])

@@

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & last.game.loc != team], 
             type = 'response')
p <- ifelse(p < .45, 0, 1)
table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & last.game.loc != team, outcome])

<<>>=

require(lubridate)

lines[, tpa := team.pts.admitted - mean(team.pts.admitted), by = list(team, season)]
lines[, tps := team.pts.scored   - mean(team.pts.scored), by = list(team, season)]

lm(tpa ~ last.game.time:party + I(hour(date))  + nhours.lgame, data = lines[nhours.lgame <= HOURS & last.game.loc != team]) %>% summary
#lm(tps ~ party, data = lines) %>% summary

lines[nhours.lgame <= 36, mean(tpa), by = last.game.loc][order(V1)]
lines[nhours.lgame <= 36, mean(tps), by = last.game.loc][order(V1)]
lines[nhours.lgame <= 36, mean(tps) - mean(tpa), by = last.game.loc][order(V1)]

HOURS <- 24
lines[, party := ifelse(nhours.lgame <= HOURS, nmusicians / log(population), 0)]
m <- glm(outcome == 'W' ~ party + nhours.lgame + travel.dist + avg.age, 
         data = lines[season < 2017 & last.game.loc != team])
